More straightforward movement variable definitions

### 2024-02-22 scripts/01.2_categorizeMovement.qmd
Showed new space use PC variable against individual vars

@@

```{r}
#| message: false
#| warning: false
cor <- round(cor(red$roost_div, red$space_use), 2)
red %>%
  ggplot(aes(x = roost_div, y = space_use))+
  geom_point(color = "chartreuse3")+ geom_smooth(method = "lm", col = "chartreuse3")+ theme_minimal()+
  xlab("Roost diversification")+ ylab("Space use (log)")+
  ggplot2::annotate(geom = "text", x = 3, y = -2, label = paste0("Correlation = ", cor))
```

Finally, **log-transformed home range** and **movement** have a correlation of `r round(cor(red$space_use_log, red$movement), 2)`.

```{r}
#| message: false
#| warning: false
cor <- round(cor(red$space_use, red$movement), 2)
red %>%
  ggplot(aes(x = space_use, y = movement))+
  geom_point(color = "orange2")+ geom_smooth(method = "lm", col = "orange2")+ theme_minimal()+
  xlab("Space use (log)") + ylab("Movement")+
  ggplot2::annotate(geom = "text", x = 2.5, y = -3, label = paste0("Correlation = ", cor))
```

>>>>

space_use %>%
  rename("Home range (log-transformed)" = "homeRange_log", "CA/HR ratio" = "coreAreaFidelity") %>%
  pivot_longer(cols = c("Home range (log-transformed)", "CA/HR ratio"),
               names_to = "measure", values_to = "value") %>%
  ggplot(aes(x = space_pc1, y = value))+
  geom_point()+geom_smooth(method = "lm")+theme_minimal()+
  facet_wrap(~measure)+
  ylab("Value (scaled)")+
  theme(legend.position = "none",
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank())
```

@@

```{r}
#| message: false
#| warning: false
cor <- round(cor(red$roost_div, red$space_use), 2)
red %>%
  ggplot(aes(x = roost_div, y = space_use))+
  geom_point(color = "chartreuse3")+ geom_smooth(method = "lm", col = "chartreuse3")+ theme_minimal()+
  xlab("Roost diversification")+ ylab("Space use")+
  ggplot2::annotate(geom = "text", x = 3, y = -2, label = paste0("Correlation = ", cor))
```

Finally, **log-transformed home range** and **movement** have a correlation of `r round(cor(red$space_use, red$movement), 2)`.

```{r}
#| message: false
#| warning: false
cor <- round(cor(red$space_use, red$movement), 2)
red %>%
  ggplot(aes(x = space_use, y = movement))+
  geom_point(color = "orange2")+ geom_smooth(method = "lm", col = "orange2")+ theme_minimal()+
  xlab("Space use") + ylab("Movement")+
  ggplot2::annotate(geom = "text", x = 2.5, y = -3, label = paste0("Correlation = ", cor))
```
